Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spanning 500\,Parsecs

### 2021-03-29 cluster_paper/ms.tex
update ms

\begin{figure*}[t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f8a.pdf}
			\includegraphics[width=0.5\textwidth]{f8b.pdf}
		}
	%		\includegraphics[width=0.7\textwidth]{f8a.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ 
  {\bf Members of \cn\ exist hundreds of parsecs from the core,
  and up to $\approx$5\kms\ from the core in tangential velocity.}
  Halo members that meet both kinematic and rotational membership
  criteria (``Subset~$\mathcal{A}$'') are shown in blue.  Halo members for which rotation periods
  should have been detectable, but were not detected, are shown in
  orange.  
  The plotted stars are restricted to $0.5<(Bp-Rp)_0<1.2$.
  The {\it left panels} show galactic coordinates and
  2D-tangential velocity space, after
  correcting for projection effects
  (Appendix~\ref{app:vproj}).
  The histogram on the right bins versus 3D separation from the core
  and 2D velocity difference.  Bins have width 25\,pc in position, and
  1.0\,km\,s$^{-1}$ in velocity.  {\bf Uncertainties in the fraction
  are taken as the quadrature sum of the rel unc of the numerator and
  denominator (FIXME)}
  \label{fig:physical_x_rotn}
	}
\end{figure*}

@@

  \paragraph{Slow sequence and fast sequence}
  %Why is there a slow and fast sequence?
  Slow: Skumanich spindown, Weber and Davis magnetic braking.
  This doesn't explain everything.
  Core envelope decoupling handwaves away the fast rotators? (Irwin,
  Aigrain, Monitor).
  Another fast rotator explanation: Naoz's merging of giant planets
  (could explain some fraction of the fast rotators -- not all of them).

>>>>

\begin{figure*}[t]
	\begin{center}
		\subfloat{
			\includegraphics[width=0.5\textwidth]{f8a.pdf}
			\includegraphics[width=0.5\textwidth]{f8b.pdf}
		}
	%		\includegraphics[width=0.7\textwidth]{f8a.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ 
  {\bf Members of \cn\ exist hundreds of parsecs from the core,
  and up to $\approx$5\kms\ from the core in tangential velocity.}
  Halo members that meet both kinematic and rotational membership
  criteria (Subset~$\mathcal{A}$) are shown in blue.  Halo members for which rotation periods
  should have been detectable, but were not detected, are shown in
  orange.  
  The plotted stars are restricted to $0.5<(Bp-Rp)_0<1.2$.
  The {\it left panels} show galactic coordinates and
  2D-tangential velocity space, after
  correcting for projection effects
  (Appendix~\ref{app:vproj}).
  The histogram on the right bins versus 3D separation from the core
  and 2D velocity difference.  Bins have width 25\,pc in position, and
  1.0\,km\,s$^{-1}$ in velocity.  {\bf Uncertainties in the fraction
  are taken as the quadrature sum of the rel unc of the numerator and
  denominator (FIXME)}
  \label{fig:physical_x_rotn}
	}
\end{figure*}

@@

  \paragraph{Slow sequence and fast sequence}
  %Why is there a slow and fast sequence?
  Slow: Skumanich spindown, Weber and Davis magnetic braking.
  This doesn't explain everything.
  Originally described as ``interface / convective'' dynamo for each.
  Now disfavored (but why?).
  Core envelope decoupling handwaves away the fast rotators? (Irwin,
  Aigrain, Monitor).
  Another fast rotator explanation: Naoz's merging of giant planets
  (could explain some fraction of the fast rotators -- not all of them).
  Tim Brown, ``metastable dynamo''?

  Perhaps most compelling: some kind of binary related explanation.
  Gillen+20 in Blanco-1 found most of them to be photometric binaries.
  Simonian+19 in the Kepler field found most rapid rotators to have
  photometric excesses.
